---
title: "Order Blend Accuracy - Plant Comparison"
output: html_document
---
## Load Packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

install.packages("read_excel")

library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(readxl)
library(ggQC)
library(sm)
library(skimr)
library(qwraps2)
library(lattice)
library(reshape2)
```

## Import Data
Run R scripts created to clean and organize data for each plant.  

```{r}
source('Order Blend Accuracy - P1.R')
source('Order Blend Accuracy - P2.R')

```
P1 has quite a bit more data than P2 as it sees more production than P2. 
Considerably more data was removed from P2. P2 is a new system and has had issues setting up reliable data collection. See notebook on P2 data collection analysis. 
Such facts should be considered with all conclusions. 

```{r}

head(ByingredP2)
head(ByingredP1)

```

Combine data for plotting.

```{r}
#Create Site column to identify which plant data comes from
ByingredP1$Site <- "P1"
ByingredP2$Site <- "P2"

ByingredP1[setdiff(names(ByingredP2), names(ByingredP1))] <- NA
ByingredP2[setdiff(names(ByingredP1), names(ByingredP2))] <- NA

#Combine all data
iByingredAll <- merge(x = ByingredP1, y = ByingredP2, all = TRUE)

#Remove na in key KPI column
ByingredAll <- iByingredAll[!is.na(iByingredAll$OrderDiff_inPerc),]

```
<P style="page-break-before: always">

##General Comparison

##Comparision by Order Size

```{r}
ggplot(data=ByingredAll)+ geom_point(aes(x=ByingredAll$EndTime, y=ByingredAll$OrderDiff_inPerc,color= ByingredAll$Site, size = ByingredAll$ActTotalOrderWt))+  
  #coord_cartesian(ylim=c(-5, 5)) +
  ggtitle("Error with Point Size on Actual Order Size")

```

P2 looks to have a tighter error range.
For P1 smaller orders have more errors. This is could be because when there is a small order weight, the order was aborted. 

```{r}

ggplot(data=plotdata1)+ geom_point(aes(x=plotdata1$EndTime, y=plotdata1$OrderDiff_inPerc,color= plotdata1$Site, size = plotdata1$IngredWeight))+
  #coord_cartesian(ylim=c(-10, 10)) +
  ggtitle("Error with Point Size on Actual Ingredient Size")

```

Smaller ingredients seem to have a greater difference in total order percent. This is the opposite of what we would expect since this would mean a much greater % of the addition. 

```{r}
ggplot(data=ByingredAll)+ geom_density(aes(x=ByingredAll$OrderDiff_inPerc,y = ..scaled.., color= ByingredAll$Site), bw= .1)+
  coord_cartesian(xlim=c(-.75, .75))


```

Both plants show a difference distribution centered around 0 indicating errors even out more or less. 
P1 has a slightly wider distribution than P2.
These conclusions are shown by the error bar plot.

```{r}
ggplot(data= ByingredAll, aes(x=ByingredAll$Site, y=abs(ByingredAll$OrderDiff_inPerc))) +
  stat_summary(fun.data = mean_se, geom = 'errorbar', position = 'dodge')+
  ggtitle("Absolute Value of Error - Errorbars")



```

##Comparision By Ingredient

Allowable deviation of actual ingredient % of blend from target ingredient % of blend is specified diffently for three ranges depending on ingredient percent of total.
```{r}
#Assign size factors for ingredients
ByingredAll$Size [ByingredAll$TarPercbyFirst <= 1] = "Small"
ByingredAll$Size [ByingredAll$TarPercbyFirst < 3 & ByingredAll$TarPercbyFirst > 1] = "Med"
ByingredAll$Size [ByingredAll$TarPercbyFirst >= 3] = "Large"
ByingredAll$Size = factor(ByingredAll$Size)

```



```{r}
ggplot(data=ByingredAll)+ geom_point(aes(x=ByingredAll$EndTime, y=ByingredAll$OrderDiff_inPerc,color= ByingredAll$Site))+ 
  #coord_cartesian(ylim=c(-5, 5))+
  facet_grid(rows = vars(Size))


```

Let's take a detailed look for each ingredient.

```{r}

plot1 <- ggplot(data=plotdata1)+ geom_point(aes(x=plotdata1$EndTime, y=plotdata1$OrderDiff_inPerc,color= plotdata1$Site, size = plotdata1$IngredWeight))+
  facet_grid(rows = vars(MaterialID), margins = "am") +
  ggtitle("Error by Ingredient")+
  coord_cartesian(ylim=c(-5, 5))

ggsave("Deviation from Target Ingredient Percent by Ingredient Plot.pdf", plot = last_plot(), height = 40 , width = 7 , device = NULL)


```


```{r}
ggplot(data= ByingredAll, aes(x=factor(ByingredAll$MaterialID), y=abs(ByingredAll$OrderDiff_inPerc),color= ByingredAll$Site)) +
  stat_summary(fun.data = mean_se, geom = 'errorbar', position = 'dodge')+
  #stat_summary(fun.y = "mean", colour = "red", size = 2, geom = "point")+
  #coord_cartesian(ylim=c(0, .2))+
  theme(axis.text.x=element_text(angle = -90, hjust = 0))+
  ggtitle("Absolute Value of Error by Ingredient - Errorbars")


```

Averages errors is higher and wider standard deviations as was expected from the scatter plots by ingredient. 
This is true to a varying degree depending on ingredient. Such observations may provide insight as to why P1 system is less accurate. 








